### 2013-06-24 trunk/network-science/paper.tex

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploited the basic form of
quantification to concentrate on specific features of the whole graph, or an
individual vertex. Our work is to promote this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph.  The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but refer to the activity instead.

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities\cite{newman2010networks}, such as
PageRank algorithm\cite{page1999pagerank}, and there are many useful network
analysis algorithms that used some kind of graph centralities. However, most
social networks change over time, and even more unfortunately, many of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limit the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an intuitive
level, the node connected with more higher activity nodes should be more
important at that time, even if other node have much more silent neighbors. If
we do not excavate the information on the time dimension, we will lose
tremendous information and also the possibility of accumulative computation
which could be helpful in enhancement the speed of answering consistent
querying.

In section 3 we will concentrate on centrality and activity in evolving social
network. We will define what centrality or activity is good, and we will design
some instance of those metrics by the standard we set. In section 4, we will
give the algorithms to compute our designed centrality and activity from the
online data structure which maintains the evolving social network. We will also
show how to quickly locate significant vertices that has high activity or
centrality at a specific time. In section 5, we will show the metrics make
sense with real world data.

\subsection{Algorithms}
Graph theory is very successful on storing and solving various problems on
static networks, we have sophisticated methodology on finding the shortest
paths, get a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
And we also have a well-established theoretical system to study problems that
do not seems to have perfect solutions. However, dynamic online queries can be
very hard for general graphs. Best known solutions for many dynamic basic graph
problems still remain unsatisfiable for general demands. So to design metrics
for an general evolving network is a very challenging and open problem. We
concentrate on the popular studied social networks and try to create meaningful
and available approaches of operation on such networks.

In section 2 we will discuss the known properties of a typical social network,
which could be helpful for our algorithm designs. In section 4, we will
establish a framework of data structure and algorithms to solve series of
possible queries including computing the metrics about a evolving social
network.

\section{Evolving Social Network}
In some related research on evolving graphs, the time dimension is represented
by constructing a sequence of graphs $EG=\{G_t(V_t,E_t)\}$ on different time
spots $t$. This model is highly expressive and universal in mathematical
statement, thus we adopt in. However, we constrain the relation of
time-adjacent graphs in order to simplify the analysis and remain the highest
possible loyalty to the real data generation. We build the \textbf{pure growing
model}, which care about the new connection forming among vertices, neglecting
the anti-growing operations such as edge deletions. We assume the existence of
every connection will contribute to the metrics, even if the connection is
later erased, so we do not delete edges or nodes in our model, instead we could
add an decay mechanism to reduce the affect of old formed links, which will be
discussed in the next section. Note that in pure growing model, we will assign
every edge a timestamp, namely when the edge is created. And thus there could
be more than one edges between a pair of nodes, with different timestamp.

\subsection{Definition}
\begin{definition}
A \textbf{pure growing model} for an evolving graph $EG$ is defined in pair:
\begin{equation}
EG=(V,E),
\end{equation}
where $V$ is the set of all nodes in the network, and $E$ is the set of edges,
formally an edge $e\in E$ for $e=(u,v,t)$, where $u,v\in V$ are the two end
points of the edge, $u<v$ (to ensure bidirectional), $t\in \mathbb{N}$. The $t$
component stored the forming time of the graph. As for weighted evolving graph
model, we modifies $e\in E$ for $e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands
for the multiplicity of the edge, which might be useful in some circumstances,
and the others stay the same meaning. In the unweighted case, we can simply set
$w=1$ for all edges.
\end{definition}

>>>>

\subsection{Dynamic Metrics}
Networks contain too much information to be easily observed by people without
any abstraction. To study a network, people exploit the basic form of
quantification to concentrate on specific features of the whole graph or an
individual vertex. Our work is to extend this method to the dynamic graphs. We
basically design new dynamic metrics according to existing successful static
ones, but we will point out a important metric that can be only observed in
time evolving networks, the activity. Intuitively speaking, a vertex with high
activity indicates more frequent recent social actions, and the vertex is more
willing to make new change by the structural sense of graph. The accuracy of
activity will be quite vital to recommendation algorithms of advertisement, new
friends, or search results. Activity can be also used by other metrics, so that
the computation of other metrics will no longer need the time information
directly, but refer to the activity instead.

Centrality, usually defined on vertices, is frequently used to measure the
importance of a specific node in graphs of all kinds. There are many previous
studies about the static graph centralities\cite{newman2010networks}, such as
PageRank algorithm\cite{page1999pagerank}, and there are many useful network
analysis algorithms that used some forms of graph centralities. However, most
social networks change over time, and even more unfortunately, many of the
networks are large-scaled, which could make the analysis become hard and
costly, hence limiting the scale of meaningful data mining. Moreover, the time
effect can also become a factor of the centrality, that is, the same graph with
different evolving sequence may have totally different metrics. On an intuitive
level, the node connected with more higher activity nodes should be more
important at that time, even if other node have much more silent neighbors. If
we do not excavate the information on the time dimension, we will lose
tremendous information and also the possibility of accumulative computation
which could be helpful in enhancing the speed of answering consistent
querying.

In section 3 we will concentrate on centrality and activity in evolving social
network. We will define what kind of activity is good, and we will design
an instance of those metrics by the standard we set. In section 4, we will
give the algorithms to compute our designed centrality and activity from the
online data structure which maintains the evolving social network. We will also
show how to quickly locate significant vertices that has high activity or
centrality at a specific time. In section 5, we will show the metrics make
sense with real world data.

\subsection{Algorithms}
Graph theory is very successful on storing and solving various problems on
static networks. We have sophisticated method on finding the shortest
paths, getting a minimal spanning tree, finding the maximal $S$-$T$ flow, etc.
And we also have a well-established theoretical system to study problems that
do not seems to have perfect solutions. However, dynamic queries can be
very hard for general graphs. Best known solutions for many dynamic basic graph
problems still remain unsatisfiable for general demands. So to design metrics
for a general evolving network is a challenging and open problem. We
concentrate on the popularly studied social networks and try to create meaningful
and available approaches of operations on such networks.

In section 2, we will discuss the known properties of a typical social network,
which could be helpful for our algorithm designs. In section 4, we will
establish a framework of data structure and algorithms to solve series of
possible queries including computing the metrics about an evolving social
network.

\section{Evolving Social Network}
In some related research on evolving graphs, the time dimension is represented
by constructing a sequence of graphs $\{G_t(V_t,E_t)\}$ on different time
spots $t$. This model is highly expressive and universal in mathematical
statement, thus we adopt in. However, we constrain the relation of
time-adjacent graphs in order to simplify the analysis and remain the highest
possible loyalty to the real data generation. We build the \textbf{pure growing
model}, which cares about the new connection forming among vertices, neglecting
the anti-growing operations such as edge deletions. We assume the existence of
every connection will contribute to the metrics, even if the connection is
later erased. So we do not delete edges or nodes in our model, instead we could
add an decay mechanism to reduce the affect of old formed links, which will be
discussed in the next section. In pure growing model, we will assign every edge
a timestamp, namely what time the edge is created. Thus there could be more
than one edges between a pair of nodes with different timestamps.

\subsection{Definition}
\begin{definition}
A \textbf{pure growing model} for an evolving graph $G$ is defined in pair:
\begin{equation}
G=(V,E),
\end{equation}
where $V$ is the set of all nodes in the network, and $E$ is the set of edges.
For every $(u,v,t)\in E$, where $u,v\in V$ are the two end
points of the edge, ($u<v$ in case of bidirectional graph),
$t\in \mathbb{N}$. The $t$
component stored the forming time of the graph. As for weighted evolving graph
model, we modifies $e\in E$ for $e=(u,v,t,w)$, where $w\in\mathbb{R}^+$ stands
for the multiplicity of the edge, which might be useful in some circumstances,
and the others stay the same meaning. In the unweighted case, we can simply set
$w=1$ for all edges.
\end{definition}
